Spatial Analysis of Russian Law Firms Naming

### 2024-07-19 law-firms-names/Paper.Rmd
Write paragraphs about vectors, YandexGPT, concrete techniques, and other important consideration about methods, #4

Question 1 (Q1) is whether the neighboring regions have more similar law firm names that regions that do not share a common border. Question 2 (Q2) is a continuous extension of Q1: whether the geographical proximity of regions has an impact on the similarity of law firm names, i.e. whether the regions that are close to each other have more similar names, and vice versa. Question 3 (Q3) moves up from the level of regions to the level of economic regions: whether names withing the economic region are more similar compared to the names outside the region. Question 4 (Q4) is what naming strategies exist in Russia and how they are spatially organized. Question 5 (Q5) is a follow-up from the previous: are there strategies common or different within each economic region?

@@

>>>>

Question 1 (Q1) is whether the neighboring regions have more similar law firm names that regions that do not share a common border. Question 2 (Q2) is a continuous extension of Q1: whether the geographical proximity of regions has an impact on the similarity of law firm names, i.e. whether the regions that are close to each other have more similar names, and vice versa. Question 3 (Q3) moves up from the level of regions to the level of economic regions: whether names within the economic region are more similar compared to the names outside the region. Question 4 (Q4) is what naming strategies exist in Russia and how they are spatially organized. Question 5 (Q5) is a follow-up from the previous: are there strategies common or different within each economic region?

@@

Text embedding, or vector, is a numeric representation of a word, sentence or a document usually designed to catch the meaning of the text. An embedding typically looks like just a sequence of decimals with fixed length, i.e. the count of elements in this sequence does not depend on the length of the input text, so that a short sentence or an entire paragraph are represented as a sequence of, say, 256 numbers. Vectors allow simple computations to find out whether they are more or less similar to each other, and the similarity of vectors corresponds to the similarity of texts. Thus, by computing a mathematical distance between embeddings, one can conclude about the semantic distance between texts. This is right the case of firm names comparison, similarity, and grouping.

There are various methods of obtaining embeddings for different texts, e.g. Word2Vec, GloVe, FastText. The newest GPT-based pretrained large language models such as ChatGPT are also capable of producing text vectors. For this study, embeddings from YandexGPT model were used. These embeddings were obtained for each unique firm name via public API of the model. The vector dimensionality is 256, i.e. each vector is a sequence of 256 numbers. All the concrete hypothesis testing techniques outlined in the next subsection are based on the use of these vectors.

### 2.2.3. Hypothesis testing

To answer Q1, firm names vectors by each region were averaged so that all names of a region are represented with a single vector that equals to the mathematical mean of all firm names vectors within this region. All regions are divided into two groups depending on the presence of common border between them. Pairwise distances between all the regions are calculated, and then median distance between regions in each of two groups is calculated. The results are additionally visualized as a box plot. It is expected that median distance between neighboring regions is smaller than median distance between regions that do not have a same border.

The similar technique is used for Q2. Again, the mean vector of all firm names for each region is computed, and pairwise semantic distance between regions is calculated. Then, a geographical distance between the centroids of regions is also measured. A correlation between geographical distance and semantic distance is computed, and the result is plotted. It is expected that the coefficient of correlation is positive.

Q3 also builds upon the pairwise semantic distances between regions. After these distances are found out, regions are grouped by economic regions. For each economic region, two metrics are calculated: the first is a median distance between regions within this econoimic region, and the second is a median distance between regions within and without this economic region. It is expected that within-median-distance is smaller that beyond-median-distance. The results are additionally illustrated on a boxplot.

Q4 and Q5 follow a slightly different methodics. First, all firm names are clustered with KMeans algorithm (number of clusters is 50). After clustering, a random sample of names from each cluster is taken, and these names are manually checked, described and tagged with the labels of more broad groups. Then these manually defined groups are assigned to names using clusters as links between groups and individual names. The number of names belonging to each group in each region is calculated, and the results of this calculation are mapped on a tile-grid map of Russia to analyze the spatial properties of grouping. In this way, Q4 is processed. For Q5, the regions are marked with the label of the most popular group, and the number of regions with different groups within an economic region is counted. It is expected that each economic regions is characterized with only one majority group. It may be the same as the group for another economic region, but a small if any variation is expected within an economic region to prove its integrity. Also, in general it is expected that there are several clear and meaningful firm naming groups, or naming strategies, and that these groups may have (or not) some clear geographical patterns.

### 2.2.4. Other important considerations

The time range of the source data is from 2016 to 2023. Only the firms that have existed for at least 3 years are included in the analysis. Only organizations are studied, while individual entrepreneurs are omitted, because they do not have firm names. Firm names are preprocessed to remove any parts pointing to the legal form of the business (e.g. limited liability company or public stock company), because these parts are common to the majority of names and thus do not add anything valuable. Law firms are selected by filtering using the following condition: main activity code equals 69.10 (activity in the area of law according to All-Russia Classifier of Kinds of Economic Activity). This filtering technique is derived from @Moiseeva2016.
